---
title: 'Reproducible Research: Peer Assessment 1'
output:
html_document:
keep_md: yes
word_document: default
---
This report is about the personal activity data analysis by finding the patterns. The raw data is recording by monitoring devices such as Fitbit, Nike Fuelband, or Jawbone Up. This report not only includes several figures to indicate the key result but also contain the processing code that makes this research reproducible.

## Loading and preprocessing the data
Unzip the file and glance at the data.
```{r echo=TRUE}
unzip('activity.zip')
ori_data<- read.csv(file = 'activity.csv')
head(ori_data)
```

## What is mean total number of steps taken per day?
Calculate the total number of steps taken per day and visualize the data by generating a histogram. 
```{r Plot1, fig.width=10, fig.height = 4}
step_per_day<-with(ori_data,tapply(steps,date,sum,na.rm=TRUE))
par(mar=c(4,4,4,4))
hist(step_per_day,
     breaks=20,
     density = 10,
     xlab = 'Steps',
     main = 'Total number of steps taken each day')
```

```{r}
med_step<-median(step_per_day)
```
The median of total number of steps taken per day is `r med_step`
```{r}
mean_step<-mean(step_per_day)
```
The mean of total number of steps taken per day is `r mean_step`

## What is the average daily activity pattern?
Make a time serise plot below to show the pattern of daily average steps of the 5-minutes interval. The max value of steps is between 500 and 1000 intervals.
```{r, fig.width=10, fig.height = 4}
inter_mean_step<-with(ori_data,tapply(steps,interval,mean,na.rm=TRUE))
xaxis<-unique(ori_data$interval)
plot(xaxis,
     inter_mean_step,
     type = 'l',
     xlab = 'time serise of one day',
     ylab= 'average number of steps',
     main = 'Average daily active pattren')
```
The code below is to calculate the maximum number of steps in the inter_mean_step dataset. 
```{r}
df<-data.frame(time = unique(ori_data$interval), step = inter_mean_step)
max_step_time<-subset(df,step==max(df[,2]))$time
```
Across all the days in the dataset `r max_step_time` interval contains the maximum number of steps on average.  

## Imputing missing values
#### Calculate the total number of missing values in the dataset.
```{r}
total_na<-sum(is.na(ori_data[,1]))
```
There are `r total_na` NAs in the dataset

#### Create a new dataset without missing data.
```{r}
data1<-data.frame(ori_data)
for(i in 1:nrow(data1)){
        if(is.na(data1[i,1])){
                var1<-df$time==data1[i,3]
                #### Fill in all of the missing values in the dataset.
                data1[i,1]<-df[which(var1),2]
        }
}
```

#### Make a histogram of the total number of steps
```{r, fig.width=10, fig.height = 4}
sum_step_data<-with(data1,tapply(steps,date,sum))
par(mar=c(4,4,4,4))
hist(sum_step_data,
     breaks=20,
     density = 10,
     xlab = 'Steps',
     main = 'Total number of steps taken each day')
```

```{r}
med_step1<-as.integer(median(sum_step_data))
```
The median of total number of steps taken per day is `r med_step1`
```{r}
mean_step1<-as.integer(mean(sum_step_data))
```
The mean of total number of steps taken per day is `r mean_step1`
The mean and median values are differ from the estimates from the first part of the report. Imputing missing data make both the value bigger.

## Are there differences in activity patterns between weekdays and weekends?
Create a array to indicate whether a given date is weekday or weekend.
```{r}
theday<-weekdays(as.Date(ori_data[,2]))
for(i in 1:length(theday)){
        if(theday[i]=="Sunday"|theday[i]=="Saturday"){
                theday[i]<-'weekend'
        }
        else{
                theday[i]<-'weekday'
        }
}
```
Create a dataframe with a column named 'theday' with the factor type of two levels weekday and weekend.
```{r}
data2<-data.frame(ori_data)
data2$theday<-factor(theday)
```
Group steps data by the interval and theday value.
```{r}
aggdata<-aggregate(steps~theday+interval,
                   data2,
                   mean,
                   na.rm=TRUE)
```
Make a panel plot to show the difference of total steps between the weekday and the weekend.
```{r, fig.width=10, fig.height = 4}
library('lattice')
with(aggdata,xyplot(steps~interval|theday,type = 'l', layout = c(1,2)))
```

@Writen by FreeFrog 
